Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-30 paper/Paper.tex

    function DAO(
        address _curator,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minTokensToCreate,
        uint _closingTime,
        address _privateCreation
    )
    function () returns (bool success);
    function receiveEther() returns(bool);
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool __newCurator
    ) onlyTokenholders returns (uint _proposalID);
    function checkProposalCode(
        uint _proposalID,
        address _recipient,
        uint _amount,
        bytes _transactionData
    ) constant returns (bool _codeChecksOut);
    function vote(
        uint _proposalID,
        bool _supportsProposal
    ) onlyTokenholders returns (uint _voteID);
    function executeProposal(
        uint _proposalID,
        bytes _transactionData
    ) returns (bool _success);
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);
    function newContract(address _newContract);
    function changeAllowedRecipients(address _recipient, bool _allowed) external returns (bool _success);
    function changeProposalDeposit(uint _proposalDeposit) external;
    function retrieveDAOReward(bool _toMembers) external returns (bool _success);
    function getMyReward() returns(bool _success);
    function withdrawRewardFor(address _account) returns(bool _success);
    function transferWithoutReward(address _to, uint256 _amount) returns (bool success);
    function transferFromWithoutReward(
        address _from,
        address _to,
        uint256 _amount
    ) returns (bool success);
    function halveMinQuorum() returns (bool _success);
    function numberOfProposals() constant returns (uint _numberOfProposals);
    function getNewDAOAdress(uint _proposalID) constant returns (address _newDAO);
    function isBlocked(address _account) returns (bool);

    event ProposalAdded(
        uint indexed proposalID,
        address recipient,
        uint amount,
        bool newServiceProvider,
        string description
    );
    event Voted(uint indexed proposalID, bool position, address indexed voter);
    event ProposalTallied(uint indexed proposalID, bool result, uint quorum);
    event NewServiceProvider(address indexed _newServiceProvider);
    event AllowedRecipientAdded(address indexed _recipient);
}

@@

\subsubsection*{transferPaidOut}
This function is called when making any transfer of DAO tokens using \verb|transfer| or \verb|transferFrom| and it updates the array \verb|paidOut| to track the amount of rewards which has been paid out already, $P$, and is calculated as follows:
\begin{equation}
 P = P_{\text{from}} \cdot T_{\text{amount}} / T_{\text{from}}
\end{equation}
Here $P_{\text{from}}$ is the total amount of ether which has been paid out to the \verb|from| address (the sender), $T_{\text{amount}}$ is the amount of tokens to be transferred and $T_{\text{from}}$ the amount of tokens owned by the \verb|from| address.

@@

This process allows DAO token holders to retrieve their ether from the DAO at any time without losing out on any of the future rewards they are entitled to receive even if they choose to leave the DAO.

>>>>

    function DAO(
        address _curator,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minTokensToCreate,
        uint _closingTime,
        address _privateCreation
    )
    function () returns (bool success);
    function receiveEther() returns(bool);
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool __newCurator
    ) onlyTokenholders returns (uint _proposalID);
    function checkProposalCode(
        uint _proposalID,
        address _recipient,
        uint _amount,
        bytes _transactionData
    ) constant returns (bool _codeChecksOut);
    function vote(
        uint _proposalID,
        bool _supportsProposal
    ) onlyTokenholders returns (uint _voteID);
    function executeProposal(
        uint _proposalID,
        bytes _transactionData
    ) returns (bool _success);
    function splitDAO(
        uint _proposalID,
        address _newCurator
    ) returns (bool _success);
    function newContract(address _newContract);
    function changeAllowedRecipients(address _recipient, bool _allowed) external returns (bool _success);
    function changeProposalDeposit(uint _proposalDeposit) external;
    function retrieveDAOReward(bool _toMembers) external returns (bool _success);
    function getMyReward() returns(bool _success);
    function withdrawRewardFor(address _account) returns(bool _success);
    function transferWithoutReward(address _to, uint256 _amount) returns (bool success);
    function transferFromWithoutReward(
        address _from,
        address _to,
        uint256 _amount
    ) returns (bool success);
    function halveMinQuorum() returns (bool _success);
    function numberOfProposals() constant returns (uint _numberOfProposals);
    function getNewDAOAdress(uint _proposalID) constant returns (address _newDAO);
    function isBlocked(address _account) returns (bool);

    event ProposalAdded(
        uint indexed proposalID,
        address recipient,
        uint amount,
        bool newCurator,
        string description
    );
    event Voted(uint indexed proposalID, bool position, address indexed voter);
    event ProposalTallied(uint indexed proposalID, bool result, uint quorum);
    event NewCurator(address indexed _newCurator);
    event AllowedRecipientAdded(address indexed _recipient);
}

@@

\subsubsection*{transferPaidOut}
This function is called when making any transfer of DAO tokens using \verb|transfer| or \verb|transferFrom| and it updates the array \verb|paidOut| to track the amount of rewards which has been paid out already, $P$, and is calculated as follows:
\begin{equation}
 P = P_{\text{from}} \cdot T_{\text{amount}} / T_{\text{from}}
\end{equation}
Here $P_{\text{from}}$ is the total amount of ether which has been paid out to the \verb|from| address (the sender), $T_{\text{amount}}$ is the amount of tokens to be transferred and $T_{\text{from}}$ is the amount of tokens owned by the \verb|from| address.

@@

This process allows DAO token holders to retrieve their ether from the DAO at any time without losing out on any of the future rewards.They are entitled to receive even if they choose to leave the DAO.
